Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-18 talk/pepm2011/paper.tex
stop using the graphic for the traces

\begin{figure}
\includegraphics{figures/step1.pdf}
\caption{Resulting Trace After Allocation Removal}
\label{fig:step1}
\end{figure}

>>>>

\begin{figure}
\begin{lstlisting}[mathescape]
# arguments to the trace: $p_{0}$, $p_{1}$
guard_class($p_1$, BoxedInteger)
$i_2$ = getfield($p_1$, intval)
guard_class($p_0$, BoxedInteger)
$i_3$ = getfield($p_0$, intval)
$i_4$ = int_add($i_2$, $i_3$)
$i_9$ = int_add($i_4$, -100)

guard_class($p_0$, BoxedInteger)
$i_{12}$ = getfield($p_0$, intval)
$i_{14}$ = int_add($i_{12}$, -1)

$i_{17}$ = int_gt($i_{14}$, 0)
guard_true($i_{17}$)

$p_{15}$ = new(BoxedInteger)
setfield($p_{15}$, intval, $i_{14}$)
$p_{10}$ = new(BoxedInteger)
setfield($p_{10}$, intval, $i_9$)

jump($p_{15}$, $p_{10}$)
\end{lstlisting}
\caption{Resulting Trace After Allocation Removal}
\label{fig:step1}
\end{figure}
